Paper 1

### 2022-07-15 scripts/Paper 1.Rmd
add windrose md

GPP.summary <- input.rearranged %>% ddply(c("GSYear"), summarise,
                                       monthly.sum = sum(GPP_LT.gC))
#GPP.summary$month.name <- factor(GPP.summary$month.name, levels=c("Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", #"Apr", "May"))
GPP.summary$season <- factor(GPP.summary$season, levels=c("Winter", "Spring", "Summer", "Autumn"))

@@

```
```{r}

@@

>>>>

#GPP.summary <- input.rearranged %>% ddply(c("GSYear"), summarise,
 #                                      monthly.sum = sum(GPP_LT.gC))
#GPP.summary$month.name <- factor(GPP.summary$month.name, levels=c("Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", #"Apr", "May"))
GPP.summary$season <- factor(GPP.summary$season, levels=c("Winter", "Spring", "Summer", "Autumn"))

@@

```{r}

@@

```{r}
(ETGPP.p <- ggplot(input.rearranged, aes(x = ET, y = GPP_LT), color = GSYear) +
  geom_point(aes(color = GSYear))+
   geom_smooth(aes(color = GSYear), method = "lm")+
    #scale_color_manual(values = group.colour) +
 # scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  xlab("Daily ET (mm)")+
   ylab("GPP")+
  theme_classic())+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14))
```
